Hybrid nonlinear system identification using neural networks

### 2020-11-24 systemID_NNs.tex
ok, add things.

\begin{align*}
  \underset{u_s}{\textnormal{min}} & \quad \ell(y_s, u_s) \\
  x_s &= f(x_s, u_s)\\ 
  y_s &= h(x_s)
\end{align*}
in which $x_s$, $y_s$, $u_s$ are the state, output, and control respectively at
steady-states. For the nonlinear reactor example, the cost is chosen as
$\ell(y_s, u_s) = c_1C_{Af} - c_2C_B$, which is a measure of the raw material
cost and product profit. The Figure  
\ref{fig:cost_curves}

\begin{figure}[!h]
  \centering
  \includegraphics[page=6, width=\textwidth]{tworeac_plots_nonlin.pdf}
  \caption{Steady-state cost curve for the nonlinear plant, grey-box, black-box,
  residual, and hybrid model after training with 5 hours of data.}
  \label{fig:cost_curves}
\end{figure}

>>>>

\begin{align*}
  \underset{u_s}{\textnormal{min}} & \quad \ell(y_s, u_s) \\
  x_s &= f(x_s, u_s)\\ 
  y_s &= h(x_s)
\end{align*}
in which $x_s$, $y_s$, $u_s$ are the state, output, and control respectively at
steady-states. For the nonlinear reactor example, the cost is chosen as
$\ell(y_s, u_s) = c_1C_{Af} - c_2C_B$, which measures the raw material
cost and product profit. The Figure \ref{fig:cost_curves} shows the 
cost curves of the plant, grey-box, black-box, and hybrid model 
obtained with 8 hours of training data.

\begin{figure}[!h]
  \centering
  \includegraphics[page=6, width=\textwidth]{tworeac_plots_nonlin.pdf}
  \caption{Steady-state cost curve for the nonlinear plant, grey-box, black-box,
  and hybrid model after training with 8 hours of data.}
  \label{fig:cost_curves}
\end{figure}
